Results_setup

### 2020-05-31 src/Result_Setup.Rmd
realized total SC dataset missing some batches

load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_5.21.20.RData")
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_5.12.20.RData")
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")
#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

@@

#remove outliers
#MLH1.merge.Skel <- MLH1.merge.Skel  %>% filter(bin_size < 60000)

```{r totSC.viz4outliers, echo=FALSE}

# -- EXAMINE the ggplot scatter plots for outliers
show.tot.sc_plot <- ggplot(data= ( Total.SC_DF %>% filter(sex == "male") ), aes(y = skel_size, x=strain))+ geom_jitter()+facet_wrap(~category, scales = "free")
```

```{r tot.skel.table, echo=FALSE, eval=FALSE}
#move to setup file

#this is redundant, setup data made -- mouse.total.skel

#make sure the table is clean -- no 5

totSC.strain.av.table <- ddply(.data=mouse.total.skel, 
                 .(sex,strain),
                 summarize, 
                 ncells = sum(ncells),
                 nmice = length(unique(mouse)),

# Q1 single bivalent section

```{r Q1.single.biv_position_table, echo=FALSE, eval=FALSE}
#strain averages for single bivalent 
#
#colnames(Curated_BivData99)

@@

@@

)
#this is the table that needs melting
#but is also easy to redo by hand

@@

Q1_1CO.pos_t.test.FULL <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(species == "M.musculus") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(species == "M.musculus") )$norm.first.foci.pos)

#WSB
Q1_1CO.pos_t.test.WSB <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$norm.first.foci.pos)
#G
Q1_1CO.pos_t.test.G <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "G") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "G") )$norm.first.foci.pos)
#LEW
Q1_1CO.pos_t.test.LEW <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$norm.first.foci.pos)

@@

#Single Biv Level
#single.biv.1CO_pos_t.test <- t.test( 
 # Curated_BivData$PER_Foci_1[(Curated_BivData$subsp=="Musc")&(Curated_BivData$sex=="male")&(Curated_BivData$hand.foci.count==1)&(Curated_BivData$Rec.group==1)], 
#   Curated_BivData$PER_Foci_1[(Curated_BivData$subsp=="Musc")&(Curated_BivData$sex=="male")&(Curated_BivData$hand.foci.count==1)&(Curated_BivData$Rec.group==0)]
#  )

#t.tests for mous.av_nrm.1CO.pos 
```

@@

lmer.Q1.nrm1CO_M1 <- lmer(norm.first.foci.pos ~ subsp * sex + (1|strain), data=Q1.Foci.pos_DF, REML = TRUE)

lmer.Q1.nrm1CO_M1reduce.sex <- lmer( norm.first.foci.pos ~ subsp  +(1|strain), data=Q1.Foci.pos_DF )

lmer.Q1.nrm1CO_M1reduce.subp <- lmer( norm.first.foci.pos ~ sex  +(1|strain), data=Q1.Foci.pos_DF )

@@

#in case factors aren't ordered
#Q1.real.short_mouse_table$subsp <- factor(Q1.real.short_mouse_table$subsp, ordered = FALSE)
#Q1.real.short_mouse_table$sex <- factor(Q1.real.short_mouse_table$sex, ordered = FALSE)
#Q1.real.short_mouse_table$strain <- factor(Q1.real.short_mouse_table$strain, ordered = FALSE)

Q1.glm_F1pos_M2 <- glm(norm.first.foci.pos ~ subsp * strain * sex, data=Q1.Foci.pos_DF)

@@

Q1.glm_1CO.pos_M3 <- glm(norm.first.foci.pos ~ strain * sex, data=Q1.Foci.pos_DF)

@@

```{r Q1.IFD_Ttests, echo=FALSE, warning=FALSE, message=FALSE}
#below are calq just from 2COs, have no fear
#mean_IFD.2CO_ABS
#mean_IFD.2CO_PER

#FULL all strains
Q1.IFD.raw_FULL_t.test <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "MOLF" ) %>% filter(species == "M.musculus")  )$mean_IFD.2CO_ABS,

                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(species == "M.musculus") )$mean_IFD.2CO_ABS)
#p-value = 0.07

Q1.IFD.PER_FULL_t.test <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "MOLF" )  %>% filter(species == "M.musculus")    )$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER)
#p-value = 1e-12

@@

Q1.IFD.PER_t.test_WSB <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="WSB" ))$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="WSB"))$mean_IFD.2CO_PER)

@@

Q1.IFD.PER_t.test_LEW <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="LEW"))$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="LEW"))$mean_IFD.2CO_PER)

@@

Q1.IFD.PER_t.test_G <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="G" ))$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="G"))$mean_IFD.2CO_PER)

@@

Q1.IFD.PER_t.test_PWD <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="PWD" ))$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="PWD"))$mean_IFD.2CO_PER)

#KAZ
Q1.IFD.raw_t.test_KAZ <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$mean_IFD.2CO_ABS,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="KAZ"))$mean_IFD.2CO_ABS)

Q1.IFD.PER_t.test_KAZ <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$mean_IFD.2CO_PER,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="KAZ"))$mean_IFD.2CO_PER)

>>>>

load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_5.30.20.RData")#added SKIVE_f BiveData
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_5.21.20.RData")
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_5.12.20.RData")
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")
#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

@@

# Q1 single bivalent section and total SC

@@

mouse total sc t.tests male female (Q1)

```{r Q1.total.SC_ttests, echo=FALSE}

#mouse.total.skel

#full group
Q1.tot.SC_t.test_FM <- t.test( ( mouse.total.skel %>% filter(sex == "male") %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$mean.skel,
                    (mouse.total.skel %>% filter(sex == "female") %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ))$mean.skel  ) #<2e-16

#WSB
Q1.tot.SC_t.test_WSB <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="WSB" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="WSB"))$mean.skel)

#LEW
Q1.tot.SC_t.test_LEW <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="LEW" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="LEW"))$mean.skel)

#G
Q1.tot.SC_t.test_G <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="G" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="G"))$mean.skel)

#PWD
Q1.tot.SC_t.test_PWD <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="PWD" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="PWD"))$mean.skel)

#KAZ
Q1.tot.SC_t.test_KAZ <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="KAZ"))$mean.skel)

#SKIVE
Q1.tot.SC_t.test_SKIVE <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="SKIVE" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="SKIVE"))$mean.skel)

#MSM
Q1.tot.SC_t.test_MSM <- t.test( (mouse.total.skel %>% filter(sex == "male") %>% filter(strain =="MSM" ))$mean.skel,
                                (mouse.total.skel %>% filter(sex == "female") %>% filter(strain =="MSM"))$mean.skel)

long bivs shouldn't be compared for Q1

```{r Q1_SC.biv.short_ttest, echo=FALSE, include=TRUE}

#Q1.real.long_mouse_table -- change to Short.biv_mouse_table

#all strains -#full group
Q1_short.SC_t.test.FM <- t.test( ( Short.biv_mouse_table %>% filter(sex == "male") %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$mean_SC,
                    (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ))$mean_SC  ) #<2e-16

# WSB p-value = 0.02 (highest p val)
Q1_short.SC_t.test.WSB <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$mean_SC)

#G  p-value = 5e-04
Q1_short.SC_t.test.G <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "G") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "G") )$mean_SC)

#LEW  p-value = 0.002
Q1_short.SC_t.test.LEW <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$mean_SC)

#PWD p-value = 0.008
Q1_short.SC_t.test.PWD <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "PWD") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "PWD") )$mean_SC)

#KAZ p-value = 0.06
Q1_short.SC_t.test.KAZ <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "KAZ") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "KAZ") )$mean_SC)

#not enough y observations
#SKIVE -- not significant (kinda few )
Q1_short.SC_t.test.SKIVE <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$mean_SC,
                   (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$mean_SC)

#MSM -- no enough male measures
#Q1_short.SC_t.test.MSM <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "MSM") )$mean_SC,
#                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "MSM") )$mean_SC)

```{r Q1_SC.biv.short_ttest99, echo=FALSE, eval=FALSE}
#this show is re-dundant
#
#run t.tests for the mouse av. for reduced single bivalent datasets

#WSB
Q1_mus.av_shortSC_t.test.WSB <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$mean_SC)

#G
Q1_mus.av_shortSC_t.test.G <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "G") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "G") )$mean_SC)

#LEW
Q1_mus.av_shortSC_t.test.LEW <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$mean_SC)

#PWD
Q1_mus.av_shortSC_t.test.PWD <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "PWD") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "PWD") )$mean_SC)

#KAZ
Q1_mus.av_shortSC_t.test.KAZ <- t.test((Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "KAZ") )$mean_SC,
                           (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "KAZ") )$mean_SC)

#SKIVE - this value used in the text
#only one SKVIE female, this is breaking the test
#Q1_mus.av_shortSC_t.test.SKIVE <- t.test(

#      (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$mean_SC,
#      (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$mean_SC
#      )

```{r Q1SC_short_ratios, echo=FALSE, eval=TRUE}

#calq the different in short.biv means across sexes
#Long.biv_mouse_table

#WSB
Q1SC.mus.av.short.biv_DIFF_WSB <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$mean_SC )

#LEW
Q1SC.mus.av.short.biv_DIFF_LEW <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$mean_SC )

#G
#Q1SC.mus.av.short.biv_DIFF_G <- mean( (Q1.real.short_mouse_table %>% filter(sex == "female") %>% filter(strain == "G") )$mean_SC) / mean(  (Q1.real.short_mouse_table %>% filter(sex == "male") %>% filter(strain == "G") )$mean_SC )

#PWD
Q1SC.mus.av.short.biv_DIFF_PWD <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "PWD") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "PWD") )$mean_SC )

#KAZ
Q1SC.mus.av.short.biv_DIFF_KAZ <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "KAZ") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "KAZ") )$mean_SC )

#SKIVE
Q1SC.mus.av.short.biv_DIFF_SKIVE <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "SKIVE") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "SKIVE") )$mean_SC )

#MSM
Q1SC.mus.av.short.biv_DIFF_MSM <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "MSM") )$mean_SC) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "MSM") )$mean_SC )

#this bivData ratio is the same as mouse average
Q1SC.BivData.short.biv_DIFF_MSM <- mean( (Short.biv_mouse_table %>% filter(sex == "female") %>% filter(strain == "MSM") )$chromosomeLength) / mean(  (Short.biv_mouse_table %>% filter(sex == "male") %>% filter(strain == "MSM") )$chromosomeLength )

```{r totSC.viz4outliers, echo=FALSE, eval=FALSE}

# -- EXAMINE the ggplot scatter plots for outliers
show.tot.sc_plot <- ggplot(data= ( Total.SC_DF %>% filter(sex == "male") ), aes(y = skel_size, x=strain))+ geom_jitter()+facet_wrap(~category, scales = "free")

show.mus.tot.sc_plot <- ggplot(data= ( mouse.total.skel %>% filter(sex == "male") %>% filter(subsp == "Musc") ), aes(y = mean.skel, x=strain, color = strain))+ geom_jitter()+ scale_color_manual(values=colors_of_strains)+ facet_wrap(~subsp, scales = "free")

```{r tot.skel.table, echo=FALSE, eval=FALSE}
#move to setup file
#this is redundant, setup data made -- mouse.total.skel
#make sure the table is clean -- no 5

totSC.strain.av.table <- ddply(.data=MLH1.merge.Skel, 
                 .(sex,strain),
                 summarize, 
                 ncells = sum(ncells),
                 nmice = length(unique(mouse)),

## total sc models

where is total_SC M1?

```{r Q1.total.SC_M1, echo=FALSE}
mouse.total.skel$subsp <- factor(mouse.total.skel$subsp, ordered = FALSE)
mouse.total.skel$sex <- factor(mouse.total.skel$sex, ordered = FALSE)
mouse.total.skel$strain <- factor(mouse.total.skel$strain, ordered = FALSE)
mouse.total.skel$species <- factor(mouse.total.skel$species, ordered = FALSE)

#mouse.total.skel
Q1.lmer_totSC_M1 <- lmer(mean.skel ~ subsp * sex + (1|strain), data= ( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

Q1.lmer_totSC_M1_R.sex <- lmer(mean.skel ~ subsp + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

Q1.lmer_totSC_M1_R.subsp <- lmer(mean.skel ~ sex + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

Q1.lmer_totSC_M1_sex <- anova(Q1.lmer_totSC_M1, Q1.lmer_totSC_M1_R.sex)$`Pr(>Chisq)`[2]
Q1.lmer_totSC_M1_subsp <- anova(Q1.lmer_totSC_M1, Q1.lmer_totSC_M1_R.subsp)$`Pr(>Chisq)`[2]
Q1.lmer_totSC_M1_int <- drop1(Q1.lmer_totSC_M1, test="Chisq")$`Pr(Chi)`[2]
Q1.lmer_totSC_M1_strain <- exactRLRT(Q1.lmer_totSC_M1)$p.value

Q1.lmer_totSC_M1_results <- data.frame(sub.sp = Q1.lmer_totSC_M1_subsp, 
sex.results =  Q1.lmer_totSC_M1_sex, 
               interaction.pval = Q1.lmer_totSC_M1_int,
rand.pval = Q1.lmer_totSC_M1_strain)

```{r Q1.glm_totalSC_M2, echo=FALSE, message=FALSE}
#mouse.total.skel

Q1.glm_totSC_M2 <- glm(mean.skel ~ subsp*strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

sum.Q1.glm_totSC_M2 <- summary(Q1.glm_totSC_M2)

#sex most sig
#subsp

#straing G, LEW
#mol * sex
#G * sex
```

```{r Q1.glm_totalSC_M3, echo=FALSE, message=FALSE}

Q1.glm_totSC_M3 <- glm(mean.skel ~ strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

sum.Q1.glm_totSC_M3 <- summary(Q1.glm_totSC_M3)
#sex most significant, 
#PWD more sig

#G, LEW, MSM, SKIVE, KAZ,  
#G*male, MSM*male

#LOT OF SIGNIFICant strain effects in this model

```{r Q1_single.Biv_M1.lmer, echo=FALSE, include=FALSE, eval=FALSE}

```{r Q1_short.M1, echo=FALSE}

Short.biv_mouse_table$subsp <- factor(Short.biv_mouse_table$subsp, ordered = FALSE)
Short.biv_mouse_table$sex <- factor(Short.biv_mouse_table$sex, ordered = FALSE)
Short.biv_mouse_table$strain <- factor(Short.biv_mouse_table$strain, ordered = FALSE)
Short.biv_mouse_table$species <- factor(Short.biv_mouse_table$species, ordered = FALSE)

Q1.lmer_short_M1 <- lmer(mean_SC ~ subsp * sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

Q1.lmer_short_M1_R.sex <- lmer(mean_SC ~ subsp + (1|strain), data= ( Short.biv_mouse_table %>%  filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

Q1.lmer_short_M1_R.subsp <- lmer(mean_SC ~ sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

Q1.lmer_short_M1_sex <- anova(Q1.lmer_short_M1, Q1.lmer_short_M1_R.sex)$`Pr(>Chisq)`[2]

Q1.lmer_short_M1_subsp <- anova(Q1.lmer_short_M1, Q1.lmer_short_M1_R.subsp)$`Pr(>Chisq)`[2]

Q1.lmer_short_M1_int <- drop1(Q1.lmer_short_M1, test="Chisq")$`Pr(Chi)`[2]

Q1.lmer_short_M1_strain <- exactRLRT(Q1.lmer_short_M1)$p.value

Q1.lmer_short_M1_results <- data.frame(sub.sp = Q1.lmer_short_M1_subsp, 
sex.results =  Q1.lmer_short_M1_sex, 
               interaction.pval = Q1.lmer_short_M1_int,
rand.pval = Q1.lmer_short_M1_strain)

Q1.glm_short.SC_M2 <- glm(mean_SC ~ subsp * strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

summ.Q1.glm_short.SC_M2 <- summary(Q1.glm_short.SC_M2)
#summ.Q1.glm_short.SC_M2$coefficients[,c(1,4)][8,]

#sex most sig
#skive, slightly sig
```

Q1.glm_short.SC_M3 <- glm(mean_SC ~ strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

#round(summ.Q1.glm_short.SC_M3$coefficients[,c(1,4)],5)
#sex male very sig -- only sig
#sum.Q1.glm_totSC_M2$coefficients[,c(1,4)][8,]

#SKIVE * male
```

```{r Q1.SC.M2plot, echo=FALSE, include=FALSE, eval=FALSE}

```{r Q1.show.SC.length, echo=FALSE, warning=FALSE, eval=FALSE}
#switch the cleanCurated_BivData

@@

@@

Q1_1CO.pos_t.test.FULL <- t.test( ( mouse.level.BivData_table %>% filter(species == "M.musculus")  %>%  filter(sex == "male") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$norm.first.foci.pos,
(mouse.level.BivData_table %>% filter(species == "M.musculus")  %>%  filter(sex == "female") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$norm.first.foci.pos ) #<2e-16

#WSB
Q1_1CO.pos_t.test.WSB <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "WSB") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "WSB") )$norm.first.foci.pos)

#G
Q1_1CO.pos_t.test.G <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "G") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "G") )$norm.first.foci.pos)
#LEW
Q1_1CO.pos_t.test.LEW <- t.test((mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain == "LEW") )$norm.first.foci.pos,
                           (mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain == "LEW") )$norm.first.foci.pos)

@@

@@

lmer.Q1.nrm1CO_M1 <- lmer(norm.first.foci.pos ~ subsp * sex + (1|strain), 
                          data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

lmer.Q1.nrm1CO_M1reduce.sex <- lmer( norm.first.foci.pos ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

lmer.Q1.nrm1CO_M1reduce.subp <- lmer( norm.first.foci.pos ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

#in case factors aren't ordered
mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = FALSE)
mouse.level.BivData_table$sex <- factor(mouse.level.BivData_table$sex, ordered = FALSE)
mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = FALSE)

Q1.glm_F1pos_M2 <- glm(norm.first.foci.pos ~ subsp * strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

Q1.glm_1CO.pos_M3 <- glm(norm.first.foci.pos ~ strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

@@

```{r Q1.IFD_Ttests_ABS, echo=FALSE, warning=FALSE, message=FALSE}
#below are calq just from 2COs, have no fear
#mean_IFD.2CO_ABS
#mean_IFD.2CO_PER

#FULL all strains
Q1.IFD.ABS_FULL_t.test <- t.test(   (mouse.level.BivData_table %>% filter(species == "M.musculus")  %>%  filter(sex == "male") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$mean_IFD.2CO_ABS,

(mouse.level.BivData_table %>% filter(species == "M.musculus")  %>%  filter(sex == "female") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )$mean_IFD.2CO_ABS    ) #0.03 (female larger)
#this comparison should be within subspecies due to strain, SC differences

@@

@@

@@

@@

#KAZ - low KAZ male curation (3 mice)
Q1.IFD.raw_t.test_KAZ <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="KAZ" ))$mean_IFD.2CO_ABS,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="KAZ"))$mean_IFD.2CO_ABS)

#SKIVE
Q1.IFD.raw_t.test_SKIVE <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="SKIVE" ))$mean_IFD.2CO_ABS,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="SKIVE"))$mean_IFD.2CO_ABS)

#MSM - 3 male 4 female measures
#only 3 MSM males
#could be missing MSM measures, (4 females, 3 males)
Q1.IFD.raw_t.test_MSM <- t.test( (mouse.level.BivData_table %>% filter(sex == "male") %>% filter(strain =="MSM" ))$mean_IFD.2CO_ABS,
                                ( mouse.level.BivData_table %>% filter(sex == "female") %>% filter(strain =="MSM"))$mean_IFD.2CO_ABS)
